### 2018-03-30 FrascatiPlot/Paper/NucleiB2.tex
minor fix to rext

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{n,p}$ their energy.
Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuteron cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.

\subsection{Full coalescence}
In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}. \textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
In this formalism, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

>>>>

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right.
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuteron cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.

\subsection{Full coalescence}
In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}. \textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as
